### 2011-02-10 paper/fitnessEvaluation.tex
parametrized -> parameterized

% Points to make:
% - linear interpolation
% - fitness reported in pixels
% - parametrized models
%   - started all on three thetas
%   - plateued at 1/3 of lifetime
% - HyperNEAT
%   - broke things a lot... so guided evolution (or in HN section?)
%   - eventually included ``shimmy''
% - finite sized window led to unfortunate bias
%
% Given earlier section, now have way of evaluating any gait g(t).
%
% Want to measure average speed, so we measure distance displaced over
% a fixed lenght run. Because we're measureing a single point on
% robot, need to start and end in same position (crouch)
% So we linearly interpolate begining (1s) and end (2s).
%
% Fitness is measured and reported directly as euclidian distance of pixels moved: equation
%
% For the parametrized models, the starting location may be important. To be as fair as possible, we picked three random points and starred all models there.
%   generally ran until 1/3 plateau
%
% For HN, couldn't do a,b,c thing, so just did three runs of length <foo>
% Things started breaking, so included shimmy to test brokenness
% penalized runs that broke servos
%
% Finite sized window kinda hurt stuff.

\acmFigg{wiiMote_crop.jpg}{robot_led_crop.jpg}{1}{A Nintendo Wii
  remote provided the location of the robot by tracking the infrared
  LED mounted on the robot's antenna.  The LED position was measured
  in pixels and transmitted from the Wii remote to the robot via
  bluetooth.}

>>>>

% Points to make:
% - linear interpolation
% - fitness reported in pixels
% - parameterized models
%   - started all on three thetas
%   - plateued at 1/3 of lifetime
% - HyperNEAT
%   - broke things a lot... so guided evolution (or in HN section?)
%   - eventually included ``shimmy''
% - finite sized window led to unfortunate bias
%
% Given earlier section, now have way of evaluating any gait g(t).
%
% Want to measure average speed, so we measure distance displaced over
% a fixed lenght run. Because we're measureing a single point on
% robot, need to start and end in same position (crouch)
% So we linearly interpolate begining (1s) and end (2s).
%
% Fitness is measured and reported directly as euclidian distance of pixels moved: equation
%
% For the parameterized models, the starting location may be important. To be as fair as possible, we picked three random points and starred all models there.
%   generally ran until 1/3 plateau
%
% For HN, couldn't do a,b,c thing, so just did three runs of length <foo>
% Things started breaking, so included shimmy to test brokenness
% penalized runs that broke servos
%
% Finite sized window kinda hurt stuff.

\acmFigg{wiiMote_crop.jpg}{robot_led_crop.jpg}{.7}{A Nintendo Wii
  remote provided the location of the robot by tracking the infrared
  LED mounted on the robot's antenna.  The LED position was measured
  in pixels and transmitted from the Wii remote to the robot via
  bluetooth.}

### 2011-02-10 paper/results.tex

The results for the gaits evolved by HyperNEAT are shown
in \figref{hnResults} and \tabref{results}.  Overall the HyperNEAT gaits
were the fastest by far, beating all the parameterized models when
comparing either average or best gaits.  We believe
that this is because HyperNEAT was allowed to explore a
much richer space of motions, but did so while still utilizing
symmetries when advantageous.
\figref{neat_110115_211410_00000_002_filt_zoom} shows a typical
HyperNEAT gait that had high fitness.  The pattern of motion is both
complex (containing multiple frequencies and repeating patterns across time)
and regular, in that patterns of multiple motors are coordinated.

>>>>

The results for the gaits evolved by HyperNEAT are shown in
\figref{hnResults} and \tabref{results}.  Overall the HyperNEAT gaits
were the fastest by far, beating all the parameterized models when
comparing either average or best gaits.  We believe that this is
because HyperNEAT was allowed to explore a much richer space of
motions, but did so while still utilizing symmetries when
advantageous.  The single best gait found during this study had a
speed of 45.72 body lengths / minute, 66\% better than the best
non-HyperNEAT gait and 8.9 times faster than the hand-coded gait.
\figref{neat_110115_211410_00000_002_filt_zoom} shows a typical
HyperNEAT gait that had high fitness.  The pattern of motion is both
complex (containing multiple frequencies and repeating patterns across
time) and regular, in that patterns of multiple motors are
coordinated.
